---
title: "stacked bar charts"
output: 
  flexdashboard::flex_dashboard:
    storyboard: true
    social: menu
    self_contained: false
---

#
```{r libraries, warning=FALSE, message=FALSE}
# required libraries
library("PKPDmisc")
library("knitr")
library("ggplot2")
library("PKPDdatasets")
library("dplyr")
library("forcats")
```

```{r globalsettings}
opts_chunk$set(fig.height = 6, fig.width = 10, dpi = 300)
```

### Final output

```{r}
ggplot(pain_score, aes(x = TRT, fill = painscore)) + 
  geom_bar(color = "black") +
  labs(title = "Pain Score Count Grouped by Treatment Administered", 
       x = "Treatment", 
       y = "Count") +
  theme_bw() +
  base_theme()
```

***

Dataset preview

```{r}
knitr::kable(head(pain_score))
```

### Step 1 - the base bar chart

@start step1
```{r}
ggplot(pain_score, aes(x = painscore)) + geom_bar()
```
@end step1

### Step 2 Reorder the data so pain score levels make sense

```{r}
pain_score <- pain_score %>% 
  mutate(painscore = fct_relevel(painscore, c("No pain relief", 
                                              "slight pain relief", 
                                              "Moderate pain relief", 
                                              "Complete pain relief"))
         )

ggplot(pain_score, aes(x = painscore)) + geom_bar()
```

***

```r
pain_score <- pain_score %>% 
  mutate(painscore = fct_relevel(painscore, c("No pain relief", 
                                              "slight pain relief", 
                                              "Moderate pain relief", 
                                              "Complete pain relief"))
         )
```

### Step 3 - Stack by treatment

@start step3
```{r}
ggplot(pain_score, aes(x = TRT, fill = painscore)) + 
  geom_bar()
```
@end step3


### Step 3 - Add black bar around each treatment group

@start step3
```{r}
ggplot(pain_score, aes(x = TRT, fill = painscore)) + 
  geom_bar(color = "black")
```
@end step3

### Step 4 - Improve layout and styling

@start step4
```{r}
ggplot(pain_score, aes(x = TRT, fill = painscore)) + 
  geom_bar(color = "black") +
  labs(title = "Pain Score Count Grouped by Treatment Administered", 
       x = "Treatment", 
       y = "Count") +
  theme_bw() +
  base_theme()
```
@end step4

### Step 5 (Bonus) - Flatten graph so not stacked

@start step5
```{r}
ggplot(pain_score, aes(x = TRT, fill = painscore)) + 
  geom_bar(position = position_dodge(), color = "black") +
  labs(title = "Pain Score Count Grouped by Treatment Administered", 
       x = "Treatment", 
       y = "Count") +
  theme_bw() +
  base_theme()
```
@end step5

### Session Information for packages and such
```{r}
devtools::session_info()
```