
---
title: "Concentration time plot"
output: 
  flexdashboard::flex_dashboard:
    storyboard: true
    social: menu
    self_contained: false
---


```{r libraries, warning=FALSE, message=FALSE}
# required libraries
library("PKPDmisc")
library("knitr")
library("ggplot2")
library("PKPDdatasets")
library("dplyr")
library("forcats")
```

```{r globalsettings}
opts_chunk$set(fig.height = 6, fig.width = 10, dpi = 300)
```

```{r}
data <- dapa_IV_oral %>% filter(FORMULATION ==  "ORAL", OCC == 2)
mean_occ2 <- data %>% 
  group_by(GENDER, TAD) %>% 
  summarize(meanCONC = round(exp(mean(log(COBS))),3))

```

### Final output

```{r conctime01 }
ggplot(data, aes(x = TAD, y = COBS, 
                      group = ID)) + 
  geom_line(size = 1.05)+ 
  xlab("Time After Dose, hours") +
  ylab("Concentration, ug/mL") +
  scale_y_log10(breaks = c(1, 10 , 50, 100, 150)) +
  theme_bw() +
  base_theme() +
  geom_line(data = mean_occ2, aes(x = TAD, 
                                  y = meanCONC, 
                                  group = GENDER, 
                                  color = GENDER), size = 1.5) +
  scale_color_discrete(name="Gender", 
                       labels= c("Male", "Female")) + 
    theme(legend.justification=c(1,1), legend.position=c(1,1))
```

***

Dataset previews

```{r}
knitr::kable(head(data))
knitr::kable(head(mean_occ2))
```

### Step 1 - the base bar chart

@start step1
```{r}
ggplot(data, aes(x = TAD, y = COBS, 
                      group = ID)) + 
  geom_line()
```
@end step1

### Step 2 - Add better labels and styling, including log transform y axis

@start step2
```{r}
ggplot(data, aes(x = TAD, y = COBS, 
                      group = ID)) + 
  geom_line(size = 1.05)+ 
  xlab("Time After Dose, hours") +
  ylab("Concentration, ug/mL") +
  scale_y_log10() +
  theme_bw() +
  base_theme() 
```
@end step2

### Step 3 - Change tick locations for y axis

@start step3
```{r}
ggplot(data, aes(x = TAD, y = COBS, 
                      group = ID)) + 
  geom_line(size = 1.05)+ 
  xlab("Time After Dose, hours") +
  ylab("Concentration, ug/mL") +
  scale_y_log10(breaks = c(1, 10 , 50, 100, 150)) +
  theme_bw() +
  base_theme() 
```
@end step3

### Step 4 - Add mean conc time by gender overlay

@start step4
```{r}
ggplot(data, aes(x = TAD, y = COBS, 
                      group = ID)) + 
  geom_line(size = 1.05)+ 
  xlab("Time After Dose, hours") +
  ylab("Concentration, ug/mL") +
  scale_y_log10(breaks = c(1, 10 , 50, 100, 150)) +
  theme_bw() +
  base_theme() +
  geom_line(data = mean_occ2, aes(x = TAD, 
                                  y = meanCONC, 
                                  group = GENDER, 
                                  color = GENDER), size = 1.5)
  
```
@end step4

### Step 5 - rename and reposition legend

@start step5
```{r}
ggplot(data, aes(x = TAD, y = COBS, 
                      group = ID)) + 
  geom_line(size = 1.05)+ 
  xlab("Time After Dose, hours") +
  ylab("Concentration, ug/mL") +
  scale_y_log10(breaks = c(1, 10 , 50, 100, 150)) +
  theme_bw() +
  base_theme() +
  geom_line(data = mean_occ2, aes(x = TAD, 
                                  y = meanCONC, 
                                  group = GENDER, 
                                  color = GENDER), size = 1.5) +
  scale_color_discrete(name="Gender", 
                       labels= c("Male", "Female")) + 
    theme(legend.justification=c(1,1), legend.position=c(1,1))
```
@end step5

### Session Information for packages and such
```{r}
devtools::session_info()
```